*flippant* -- An R package for the automated analysis of dithionite scramblase

### 2016-05-03 inst/manuscript/manuscript.rmd
Finalize intra-manuscript transition away from camelCase;

and handing the function the path to the user assembled spreadsheet of input 
data (`x`). The `adjust` argument to the function call serves to selectively 
inactivate *wmtsa*-provided (see above) alignment of multiple spectra to the 
time of dithionite addition. Acquisition time coverage of the plot may be tuned 
by user-provided minimal (`time_min_sec` ) and maximal (`timeMaxSec`) time points
to be included (in seconds).

@@

```{r, eval = FALSE}
# Plot spectral traces (Figure 1A)
scramblase_assay_traces("inputTable.txt", timeMaxSec = 350)
```

@@

analysis_timing_function <- function(){
  scramblase_assay_traces(
    x,
    timeMaxSec = 350)
  scramblase_assay_plot(
    x,
    generation_of_algorithm = 1)
  scramblase_assay_plot(
    x,
    generation_of_algorithm = 1,
    split_by_experiment = FALSE)
  scramblase_assay_stats(
    x,
    generation_of_algorithm = 1, 
    split_by_experiment = FALSE)
}

>>>>

and handing the function the path to the user assembled spreadsheet of input 
data (`x`). The `adjust` argument to the function call serves to selectively 
inactivate *wmtsa*-provided (see above) alignment of multiple spectra to the 
time of dithionite addition. Acquisition time coverage of the plot may be tuned 
by user-provided minimal (`time_min_sec` ) and maximal (`time_max_sec`) time points
to be included (in seconds).

@@

```{r, eval = FALSE}
# Plot spectral traces (Figure 1A)
scramblase_assay_traces("inputTable.txt", time_max_sec = 350)
```

@@

analysis_timing_function <- function(){
  scramblase_assay_traces(
    x,
    time_max_sec = 350)
  scramblase_assay_plot(
    x,
    generation_of_algorithm = 1)
  scramblase_assay_plot(
    x,
    generation_of_algorithm = 1,
    split_by_experiment = FALSE)
  scramblase_assay_stats(
    x,
    generation_of_algorithm = 1, 
    split_by_experiment = FALSE)
}
